MPSA 2023 proposal

### 2022-10-06 manuscript/submissions/2023-mpsa.qmd
Add MPSA proposal

---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina = 3
)

library(emoji)

Title <- "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
Authors <- "Andrew Heiss and Meng Ye"
Year <- "2022"
```

# `r Title`

[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University  
Meng Ye • Andrew Young School of Policy Studies • Georgia State University

---

## Abstract

@@

---

## `r emoji::emoji_glue(":hugs::oyster:")`: "Compassionate clam" project name

Because project titles change all the time with revisions, rewriting, and peer review, we used [**codename**](http://svmiller.com/codename/) to generate an [Ubuntu-style](https://wiki.ubuntu.com/DevelopmentCodeNames) internal-to-us project name that won't change.

```{r generate-code-name, eval=FALSE}
library(codename)
codename_message()
#> code name generated by {codename} v.0.4.0

codename(seed = "china ongo law", type = "ubuntu")
#> [1] "compassionate clam"
```

## Licenses

**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/))

**Code:** All code is licensed under the [MIT License](LICENSE.md).

## Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By participating in this project you agree to abide by its terms.

>>>>

---
title: "MPSA 2023 proposal" 
date: "October 6, 2022"
author:
  - name: Andrew Heiss
    email: aheiss@gsu.edu
    orcid: 0000-0002-3948-3914
    affiliations: 
      - id: ays
        name: Georgia State University
        department: Andrew Young School of Policy Studies
        city: Atlanta
        region: GA
    attributes:
      corresponding: true
  - name: Meng Ye
    email: mye2@gsu.edu
    affiliations:
      - ref: ays
format:
  html: default
  docx: default
  pdf: default
---

# Title

*(102 characters; 250 limit)*

The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

# Brief Overview

*(244 characters; 250 limit)*

To better understand the effect of closing space for global civil society, we use administrative data collected under China’s 2017 Overseas NGO law to explore how NGO issue areas influence their operational flexibility under strict regulations.

# Keywords

*(49 characters; 250 limit)*

China, international NGO, civil society, ONGO law

# Abstract

*(1,500 characters; 1,500 limit)*

@@
